Rates and delay times of type Ia supernovae in the Dark Energy Survey

### 2021-07-06 final.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.png}
    \caption{Upper: Distribution of the stellar mass of the SN host galaxies. The raw (green dashed) and spectroscopic-efficiency-weighted (blue dot-dashed; Section \ref{subsec:incompletenss_SN_hosts}) histograms are both normalised. Comparison samples are PTF (purple; \citealt{Pan2014}) and Pantheon (orange; \citealt{Scolnic2018}). Lower: As upper but for field galaxies, and with galaxy frequency shown on a log scale.  The distribution closely matches data from the ZFOURGE survey at $0.5<z<0.75$ (magenta dots). The difference between the raw counts (grey dotted) and the $V_{\mathrm{max}}$ corrected counts (orange solid; see Section \ref{sec:incompleteness}) is minimal. 
    \label{fig:mass_hist_hosts_field}}
\end{figure}

\begin{figure}
    \centering
    %\includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
    \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies_z_x1_c.png}
    \caption{ SN detection efficiencies split by DES-SN field, $x_1$ and $c$. The $y-$axis represents the fraction of simulated SNe in a given redshift bin that would have been detected by DES-SN and passed light curve quality cuts. Lines are polynomial fits that approximate the efficiency curves. 
    \label{fig:SN_efficiency}}
\end{figure}

\begin{figure}
    \centering
    %\includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
    \includegraphics[width=0.5\textwidth]{figs/eff_z.png}
    \caption{SN host galaxy spectroscopic efficiencies as a function of redshift $z$. Efficiency curves are grouped by shallow (\{F\}12) and deep (\{F\}3) fields, and averaged over the 5 years of the survey. The lower and upper redshift limits for this analysis are indicated by $z_{\mathrm{min}}$ and $z_{\mathrm{max}}$ respectively.
    \label{fig:eff_z}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/completeness_combined.png}
    \caption{Measuring the completeness of the field galaxy sample. \textit{Upper}: the $T_{\mathrm{C}}$ galaxy completeness statistic (which is calculated by ranking objects by absolute magnitude in slices of distance modulus) as a function of apparent magnitude; \textit{middle} as per \textit{upper}, but for the $T_{\mathrm{V}}$ statistic which is measured by ranking galaxies by distance modulus in slices of absolute magnitude; \textit{lower}: the combined, normalised completeness in each band.  
    \label{fig:completeness}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/field_vmax.png}
    \caption{Distribution of $V_{\mathrm{max}}$ corrections applied to field galaxies in the DES sample in order to correct for incompleteness. The majority of galaxies have no correction, and the distribution of those that do follows a power-law.
    \label{fig:vmax_field}}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_x1_fitjoint.png}
    \caption{\textit{Upper}: Posterior samples of the fraction of "prompt" SNe resulting from the two-population fit, displayed as a function of host galaxy stellar mass. 
    \textit{Lower}: As per Fig. \ref{fig:rate_fitted_split_x1} but with the data fit simultaneously by a single two-component DTD, with fixed slope $\beta = -1$ and a prompt fraction that is 1 at short delay times, 0 at large delay times, and a linear function of time between $t_1 =0.65$~Gyr (where tardy SNe switch on) and $t_2=0.85$~Gyr (where prompt SNe turn off).%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
    \label{fig:rate_fitted_split_x1_2c_DTD}}
\end{figure}
The SN Ia rate as a function of stellar mass for SNe split by stretch is shown in Fig. \ref{fig:rate_fitted_split_x1}. The evolution of the rate with stellar mass is significantly different for the two sub-samples: high-stretch SNe dominate the rate at low stellar mass but tail off in the higher mass galaxies, while low-stretch SNe are subdominant in low mass galaxies but display a much steeper dependence on stellar mass and make up the vast majority of SNe in high-mass hosts. These measurements reflect the observed correlations of $x_1$ with stellar mass, sSFR (and by inference, stellar age) as been seen by \citet{Rigault2013,Graur2017,Rigault2018,Rose2019,Hakobyan2020,Nicolas2020,Rose2021}, as well as morphology \citep{Hakobyan2020}. The corresponding DTD fit results in a steep power-law $\beta =-1.70^{+0.19}_{-0.10}$ for high-stretch SNe indicative of a population of predominantly prompt SNe, and a much shallower decay slope ($\beta = -0.79 \pm 0.08$) for low-stretch SNe representing a much more delayed population. The difference in $\beta$ is significant at a level of $3.8\sigma$. This result provides an intriguing confirmation of that observed in 101 SDSS SNe Ia by \citet{Brandt2010} who found that low-$x_1$ SNe displayed much longer delay times than those with high $x_1$.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.pdf}
    \caption{Upper: Distribution of the stellar mass of the SN host galaxies. The raw (green dashed) and spectroscopic-efficiency-weighted (blue dot-dashed; Section \ref{subsec:incompletenss_SN_hosts}) histograms are both normalised. Comparison samples are PTF (purple; \citealt{Pan2014}) and Pantheon (orange; \citealt{Scolnic2018}). Lower: As upper but for field galaxies, and with galaxy frequency shown on a log scale.  The distribution closely matches data from the ZFOURGE survey at $0.5<z<0.75$ (magenta dots). The difference between the raw counts (grey dotted) and the $V_{\mathrm{max}}$ corrected counts (orange solid; see Section \ref{sec:incompleteness}) is minimal. 
    \label{fig:mass_hist_hosts_field}}
\end{figure}

\begin{figure}
    \centering
    %\includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.pdf}
    \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies_z_x1_c.pdf}
    \caption{ SN detection efficiencies split by DES-SN field, $x_1$ and $c$. The $y-$axis represents the fraction of simulated SNe in a given redshift bin that would have been detected by DES-SN and passed light curve quality cuts. Lines are polynomial fits that approximate the efficiency curves. 
    \label{fig:SN_efficiency}}
\end{figure}

\begin{figure}
    \centering
    %\includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.pdf}
    \includegraphics[width=0.5\textwidth]{figs/eff_z.pdf}
    \caption{SN host galaxy spectroscopic efficiencies as a function of redshift $z$. Efficiency curves are grouped by shallow (\{F\}12) and deep (\{F\}3) fields, and averaged over the 5 years of the survey. The lower and upper redshift limits for this analysis are indicated by $z_{\mathrm{min}}$ and $z_{\mathrm{max}}$ respectively.
    \label{fig:eff_z}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/completeness_combined.pdf}
    \caption{Measuring the completeness of the field galaxy sample. \textit{Upper}: the $T_{\mathrm{C}}$ galaxy completeness statistic (which is calculated by ranking objects by absolute magnitude in slices of distance modulus) as a function of apparent magnitude; \textit{middle} as per \textit{upper}, but for the $T_{\mathrm{V}}$ statistic which is measured by ranking galaxies by distance modulus in slices of absolute magnitude; \textit{lower}: the combined, normalised completeness in each band.  
    \label{fig:completeness}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/field_vmax.pdf}
    \caption{Distribution of $V_{\mathrm{max}}$ corrections applied to field galaxies in the DES sample in order to correct for incompleteness. The majority of galaxies have no correction, and the distribution of those that do follows a power-law.
    \label{fig:vmax_field}}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_x1_fitjoint.pdf}
    \caption{\textit{Upper}: Posterior samples of the fraction of "prompt" SNe resulting from the two-population fit, displayed as a function of host galaxy stellar mass. 
    \textit{Lower}: As per Fig. \ref{fig:rate_fitted_split_x1} but with the data fit simultaneously by a single two-component DTD, with fixed slope $\beta = -1$ and a prompt fraction that is 1 at short delay times, 0 at large delay times, and a linear function of time between $t_1 =0.65$~Gyr (where tardy SNe switch on) and $t_2=0.85$~Gyr (where prompt SNe turn off).%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
    \label{fig:rate_fitted_split_x1_2c_DTD}}
\end{figure}
The SN Ia rate as a function of stellar mass for SNe split by stretch is shown in Fig. \ref{fig:rate_fitted_split_x1}. The evolution of the rate with stellar mass is significantly different for the two sub-samples: high-stretch SNe dominate the rate at low stellar mass but tail off in the higher mass galaxies, while low-stretch SNe are subdominant in low mass galaxies but display a much steeper dependence on stellar mass and make up the vast majority of SNe in high-mass hosts. These measurements reflect the observed correlations of $x_1$ with stellar mass, sSFR (and by inference, stellar age) as been seen by \citet{Rigault2013,Graur2017,Rigault2018,Rose2019,Hakobyan2020,Nicolas2020,Rose2021}, as well as morphology \citep{Hakobyan2020}. The corresponding DTD fit results in a steep power-law $\beta =-1.70^{+0.19}_{-0.10}$ for high-stretch SNe indicative of a population of predominantly prompt SNe, and a much shallower decay slope ($\beta = -0.79 \pm 0.08$) for low-stretch SNe representing a much more delayed population. The difference in $\beta$ is significant at a level of $3.8\sigma$. This result provides an intriguing confirmation of that observed in 101 SDSS SNe Ia by \citet{Brandt2010} who found that low-$x_1$ SNe displayed much longer delay times than those with high $x_1$.
